### 2020-03-19 README.Rmd
minor tweeks, and commentary on Hausdorff distance

## Documentation

Please see our website at [https://skgallagher.github.io/EpiCompare/](https://skgallagher.github.io/EpiCompare/).

@@

   Currently there are 13 data sets in which to explore the different `EpiCompare` functions.  These correspond to different sources of raw data along, agent vs. aggregate format, and emphases of different processes such as vital dynamics (e.g. birth and).

@@

  - `pomp_sir` Example output from the `pomp` package.

## Example

@@

## Notes:
1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)

>>>>

@@

Description of data including in this package can be found in the data section of the [reference](https://skgallagher.github.io/EpiCompare/reference/index.html#section-data) page of the documentation website.

```{r eval = F, echo = F}
   Currently there are 13 data sets in which to explore the different `EpiCompare` functions.  These correspond to different sources of raw data along, agent vs. aggregate format, and emphases of different processes such as vital dynamics (e.g. birth and).

@@

  - `pomp_sir` Example output from the `pomp` package.
```
## Example

@@

## Package Creation Notes:
1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)
